Synthesizing Symmetric Lenses

### 2018-07-12 papers/SymmetricLenses/main.tex
space tweaks

\newif\ifdraft\drafttrue  % set true to show comments
%\newif\ifdraft\draftfalse  % set true to show comments
\newif\ifanon\anonfalse    % set true to suppress names, etc.
\newif\iffull\fullfalse   % set true for long version
\newif\ifappendices\appendicestrue

@@

\begin{figure}
  \includegraphics[width=.5\textwidth]{high-level-algorithm.pdf}
  \caption{Schematic diagram for the simple symmetric lens synthesis algorithm.
    The user provides regular expressions \BRegex and \BRegexAlt and a set of
    examples \Examples{} as input. \Expand first converts \BRegex and \BRegexAlt
    to stochastic regular expressions \Regex and \RegexAlt with default
    probabilities. It then finds pairs of stochastic regular expressions
    equivalent to \Regex and \RegexAlt and iteratively proposes them to
    \GreedySynth. \GreedySynth finds a lens typed between the supplied SREs.
    When the algorithm determines it has found a likely lens, it returns it.}
  \label{fig:high-level-algorithm}
\end{figure}

@@

As an example, consider searching for a lens between \lstinline{"" | name.name$^*$} and \lstinline{"" | name}. \GreedySynth might first pop the
sequence pair \lstinline{""} and \lstinline{""}, because there is a bijective
sequence lens between them. As neither \lstinline{""} is involved in a sequence
lens, this lens is considered useful. Next, the sequence lens between
\lstinline{name.name$^*$} and \lstinline{name} would be popped: while that lens
is not bijective: it is still better than the alternatives. As all sequences are
now involved in sequence lenses, and there are no examples to make other lenses
useful, no further sequence lenses would be added to the lens builder.

@@

\begin{figure}
  \includegraphics{generated-graphs/times}
  \caption{Number of benchmarks that can be solved by a given algorithm in a
    given amount of time. \SSOpt{} is the full symmetric synthesis algorithm.
    \SSNCOpt{} is the symmetric synthesis algorithm without using a library of
    existing lenses. The symmetric synthesis algorithm is able to complete all
    benchmarks in under 30 seconds elapsed total time. Without compositional
    synthesis it is able to complete 26. Each benchmark specification includes
    source and target regular expressions, between one and three sufficient
    examples, and, if necessary, the timing parameter determined to be
    sufficient for correctness during a prior interactive session.}
  \label{fig:times}
\end{figure}

@@

\begin{figure}
  \includegraphics{generated-graphs/times_bijective}
  \caption{Number of benchmarks that can be solved by a given algorithm in a
    given amount of time. \SSOpt{} is the full symmetric synthesis algorithm.
    \BSOpt{} is the full bijective lens synthesis algorithm.}
  \label{fig:times_bijective}
\end{figure}

\subsection{The Effects of Our Heuristics}
\label{subsec:effect-of-heuristics}
We evaluate the usefulness of (1) our information-theoretic metric, and (2) our
termination heuristic.  To this end, we run our program in several different modes:\\[1ex]
\begin{tabulary}{\linewidth}{rL}
  \AnyOpt{}: & We ignore the information-theoretic preference metric entirely,
               returning the first lens \GreedySynth finds without using this information. \\ 
  \FLOpt{}: &  \GreedySynth uses the information-theoretic preference
              metric to find a lens, and we return immediately upon finding a
              satisfying lens, instead of returning based on \Continue.  \\
  \CCOpt{}: & We replace our information-theoretic cost metric with one where
              the cost of the lens is the number of disonnects plus the number
              of merges.\\
  \ZTOpt{}: & \ZTOpt{} runs the algorithm with the termination parameter
              universally set to 0 (default). \\
  \TFTOpt{}: & \TFTOpt{} runs the algorithm with the
               termination parameter universally set to 25. \\
  \NTFTOpt{}: & \NTFTOpt{} runs the algorithm with the
                termination parameter universally set to -25. \\
\end{tabulary}

\begin{figure}
  \includegraphics{generated-graphs/metrics_importance}
  \caption{Number of benchmarks that synthesize the correct lens by a given
    algorithm. \AnyOpt{} provides no notion of cost, and merely returns the
    first lens it finds that satisfies the specification. \FLOpt{} provides a
    notion of cost to \GreedySynth, but once a satisfying lens is greedily
    found, that lens is returned. \CCOpt{} synthesizes lenses, where the cost of
    a lens is the number of disconnects plus the number of merges. \ZTOpt{} runs
    the algorithm with the termination parameter universally set to 0 (default).
    \TFTOpt{} runs the algorithm with the termination parameter universally set
    to 25. \NTFTOpt{} runs the algorithm with the termination parameter
    universally set to -25.}
  \label{fig:metric}
\end{figure}

@@

>>>>

%\newif\ifdraft\drafttrue  % set true to show comments
\newif\ifdraft\draftfalse  % set true to show comments
\newif\ifanon\anonfalse    % set true to suppress names, etc.
\newif\iffull\fullfalse   % set true for long version
\newif\ifappendices\appendicestrue

@@

\begin{figure}
  \includegraphics[width=.5\textwidth]{high-level-algorithm.pdf}
  \vspace{-2ex}
  \caption{Schematic diagram for the simple symmetric lens synthesis algorithm.
    The user provides regular expressions \BRegex and \BRegexAlt and a set of
    examples \Examples{} as input. \Expand first converts \BRegex and \BRegexAlt
    to stochastic regular expressions \Regex and \RegexAlt with default
    probabilities. It then finds pairs of stochastic regular expressions
    equivalent to \Regex and \RegexAlt and iteratively proposes them to
    \GreedySynth. \GreedySynth finds a lens typed between the supplied SREs.
    When the algorithm determines it has found a likely lens, it returns it.}
  \label{fig:high-level-algorithm}
\end{figure}

@@

As an example, consider searching for a lens between \lstinline{"" | name.name$^*$} and \lstinline{"" | name}. \GreedySynth might first pop the
sequence pair \lstinline{""} and \lstinline{""}, because there is a bijective
sequence lens between them. As neither \lstinline{""} is involved in a sequence
lens, this lens is considered useful. Next, the sequence lens between
\lstinline{name.name$^*$} and \lstinline{name} would be popped: while that lens
is not bijective it is still better than the alternatives. As all sequences are
now involved in sequence lenses, and there are no examples to make other lenses
useful, no more sequence lenses would be added to the lens builder.

@@

\begin{figure}
  \includegraphics{generated-graphs/times}
  \vspace{-4ex}
  \caption{Number of benchmarks that can be solved by a given algorithm in a
    given amount of time. \SSOpt{} is the full symmetric synthesis algorithm.
    \SSNCOpt{} is the symmetric synthesis algorithm without using a library of
    existing lenses. The symmetric synthesis algorithm is able to complete all
    benchmarks in under 30 seconds elapsed total time. Without compositional
    synthesis it is able to complete 26. Each benchmark specification includes
    source and target regular expressions, between one and three sufficient
    examples, and, if necessary, the timing parameter determined to be
    sufficient for correctness during a prior interactive session.}
  \label{fig:times}
\end{figure}

@@

\begin{figure}[t]
  \includegraphics{generated-graphs/times_bijective}
  \vspace{-4ex}
  \caption{Number of benchmarks that can be solved by a given algorithm in a
    given amount of time. \SSOpt{} is the full symmetric synthesis algorithm.
    \BSOpt{} is the full bijective lens synthesis algorithm.}
  \label{fig:times_bijective}
\end{figure}

\subsection{The Effects of Our Heuristics}
\label{subsec:effect-of-heuristics}
We evaluate the usefulness of (1) our information-theoretic metric, and (2) our
termination heuristic.  To this end, we run our program in several different modes:\\[1ex]
\begin{tabulary}{\linewidth}{rL}
  \AnyOpt{}: & We ignore the information-theoretic preference metric entirely,
               returning the first lens \GreedySynth finds without using this information. \\ 
  \FLOpt{}: &  \GreedySynth uses the information-theoretic preference
              metric to search, but returns immediately upon finding a
              satisfying lens, instead of returning based on \Continue.  \\
  \CCOpt{}: & We replace our information-theoretic cost metric with one where
              the cost of the lens is the number of disonnects plus the number
              of merges.\\
\end{tabulary}

\begin{tabulary}{\linewidth}{rL}
  \ZTOpt{}: & \ZTOpt{} runs the algorithm with the termination parameter
              universally set to 0 (default). \\
  \TFTOpt{}: & \TFTOpt{} runs the algorithm with the
               termination parameter universally set to 25. \\
  \NTFTOpt{}: & \NTFTOpt{} runs the algorithm with the
                termination parameter universally set to -25. \\
\end{tabulary}

@@

\begin{figure}[t]
  \includegraphics{generated-graphs/metrics_importance}
  \vspace{-4ex}
  \caption{Number of benchmarks that synthesize the correct lens by a given
    algorithm. \AnyOpt{} provides no notion of cost, and merely returns the
    first lens it finds that satisfies the specification. \FLOpt{} provides a
    notion of cost to \GreedySynth, but once a satisfying lens is greedily
    found, that lens is returned. \CCOpt{} synthesizes lenses, where the cost of
    a lens is the number of disconnects plus the number of merges. \ZTOpt{} runs
    the algorithm with the termination parameter universally set to 0 (default).
    \TFTOpt{} runs the algorithm with the termination parameter universally set
    to 25. \NTFTOpt{} runs the algorithm with the termination parameter
    universally set to -25.}
  \label{fig:metric}
\end{figure}
